Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Added label inside the plot

right_top_img <- plot_digit_img(pixels_gathered_within, palette = "Blues 2", title_text = "a", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

middle_img <- plot_digit_img(pixels_gathered_within, palette = "Greens 3", title_text = "b", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

right_bottom_img <- plot_digit_img(pixels_gathered_within, palette = "Purples 2", title_text = "c", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_outside <- plot_digit_img(pixels_gathered_outside, palette = "Grays", title_text = "d", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_inside <- plot_digit_img(pixels_gathered_inside, palette = "Oranges", title_text = "e", hjust = 0, ncol = 9) + theme(plot.margin = margin(0, 0, 0, 0))

>>>>

right_top_img <- plot_digit_img(pixels_gathered_within, palette = "Blues 2", title_text = "a", hjust = 0.17) + theme(plot.margin = margin(0, 0, 0, 0))

@@

middle_img <- plot_digit_img(pixels_gathered_within, palette = "Greens 3", title_text = "b", hjust = 0.17) + theme(plot.margin = margin(0, 0, 0, 0))

@@

right_bottom_img <- plot_digit_img(pixels_gathered_within, palette = "Purples 2", title_text = "c", hjust = 0.17) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_outside <- plot_digit_img(pixels_gathered_outside, palette = "Grays", title_text = "d", hjust = 0.17) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_inside <- plot_digit_img(pixels_gathered_inside, palette = "Oranges", title_text = "e", hjust = 0.17, ncol = 3) + theme(plot.margin = margin(0, 0, 0, 0))
